Proof nets for first-order additive linear logic

### 2018-01-21 ALL1.tex
typo fix third authors -> third author's

{\all} is of course part of {\mall} (multiplicative-additive linear logic), and its lessons are clearly visible in the second author's canonical proof nets \cite{Hughes-vanGlabbeek-2005} for that fragment, as well as the first and second author's locally canonical \emph{conflict nets}~\cite{Hughes-Heijltjes-2016}. But its proof nets also appear as the \emph{skew fibrations} in the second author's \emph{combinatorial proofs} for classical logic~\cite{Hughes-2006-proofs}, and in the third authors study of the \emph{medial rule} for classical logic~\cite{str:RTA07}. To prepare the ground for the extension of \emph{combinatorial proofs} to first-order classical logic is one motivation for the% current presentation.

>>>>

{\all} is of course part of {\mall} (multiplicative-additive linear logic), and its lessons are clearly visible in the second author's canonical proof nets \cite{Hughes-vanGlabbeek-2005} for that fragment, as well as the first and second author's locally canonical \emph{conflict nets}~\cite{Hughes-Heijltjes-2016}. But its proof nets also appear as the \emph{skew fibrations} in the second author's \emph{combinatorial proofs} for classical logic~\cite{Hughes-2006-proofs}, and in the third author's study of the \emph{medial rule} for classical logic~\cite{str:RTA07}. To prepare the ground for the extension of \emph{combinatorial proofs} to first-order classical logic is one motivation for the% current presentation.
